Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-25 tex/MesnardoBarba2019.tex
Add paragraph on University cluster, and others
Also:

* Add some sentences on user experiences with Microsoft Azure (learning curve, helper tools, Intel MPI, visible costs, quotas).

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship of $20,000$ USD in cloud credits to run CFD simulations with our in-house software.
From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges are due the usage of virtual machines.
We had the opportunity to use different instances on Microsoft Azure and most the charges for the usage of virtual machines of the \texttt{NC24r} instance (used for the two- and three-dimensional simulations of the flying snake).
The \texttt{NC24r} instance is part of the NC-series (Table \ref{tab:nc_series}); we copiously used as it enables RDMA capabilities for our MPI application and features NVIDIA K80 GPU devices.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).

@@

In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Batch Shipyard configuration files required to rerun the simulations on Microsoft Azure.
In addition, all the scripts to reproduce the figures in the present article are made available.
The reproducibility packages are hosted on GitHub in the repository \texttt{cloud-repro}.\footnote{\url{https://github.com/barbagroup/cloud-repro}}

>>>>

Universities and national laboratories can spend millions of dollars to deploy and maintain on-site high-performance computing (HPC) clusters.
At the George Washington University, we have access to a university-managed HPC cluster called Colonial One.
The cluster is now $6$ years old and approaching its end-of-life.
On average, its computational resources are idle $9\%$ of the time and unavailable to users for roughly 5 days a year (due to maintenance).
Administrators of the cluster are now considering integrating cloud-computing platforms in the landscape of HPC at the George Washington University.
Over the past decade, cloud-computing platforms have rapidly evolved, now proposing solutions for scientific applications.
From a user's point of view, a cloud platform offers great flexibility (hardware and virtual machines) with instantaneous availability of infinite (in appearance) computational resources.
No more waiting time in job-submission queues!
This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
On a public-cloud platform such as Microsoft Azure, with a "pay-as-you-go" type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters.

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship of $20,000$ USD in cloud credits to run CFD simulations with our in-house software.
We a ``pay-as-you-go'' type of subscription, users can directly sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges are due the usage of virtual machines.
We had the opportunity to use different instances on Microsoft Azure and most the charges for the usage of virtual machines of the \texttt{NC24r} instance (used for the two- and three-dimensional simulations of the flying snake).
The \texttt{NC24r} instance is part of the NC-series (Table \ref{tab:nc_series}); we copiously used as it enables RDMA capabilities for our MPI application and features NVIDIA K80 GPU devices.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).

@@

Running CFD simulations on Microsoft Azure was a first time for our research lab.
As novices in cloud computing, it took us several months to become familiar with the technical vocabulary and the infrastructure of Microsoft Azure before we could submit our first simulation of the snake.

Command-line tools such as Azure-CLI and Batch Shipyard were greatly helpful to create and submit everything from our local terminal. (In our research lab, we tend to avoid, as much as possible, interacting with graphical-user interfaces, so as to make our workflow more reproducible.)
Azure-CLI helped us to setup the Azure Batch account and its associated Azure Storage, as well as uploading/downloading our simulation data.
With Batch Shipyard, users do not need to have experience with the Azure Batch SDK.
We have used Batch Shipyard to submit jobs on Azure Batch to run Docker container-based multi-tasks.
Note that Batch Shipyard also support Singularity containers.

Our in-house CFD research software makes use of the MPI library to run applications on distributed-memory architectures.
We used Azure instances that feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over an InfiniBand network.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.

Moreover, Microsoft Azure implements quotas, such as the maximum number of cores that can be used in a certain region.
To run our simulations, we had to open online customer support requests every time we wanted to increase our core quota for a subscription, with a certain service in certain region with a certain type of instances.
We had to go through this process at least five times during our sponsorship period.

In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Batch Shipyard configuration files and instructions required to rerun the simulations on Microsoft Azure.
In addition, all the scripts to reproduce the figures in the present article are made available.
The reproducibility packages are hosted on GitHub in the repository \texttt{cloud-repro}.\footnote{\url{https://github.com/barbagroup/cloud-repro}}
